Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-12 manuscript/supplemental_material.Rnw
currently transcript mapping is in the main text

\begin{figure}
<<transcriptome.mapping.figure,fig.width=8,fig.height=8,echo=FALSE>>=
star.logs.unmapped <- 
    star.logs[grepl("%",field) & 
                  grepl("unmapped",field) & 
                      !grepl("too many mismatches",field),]
star.logs.unmapped <- 
    star.logs.unmapped[,field:=capfirst(gsub("\\% of reads unmapped: ","",field))]
pushViewport(viewport(layout=grid.layout(ncol=1,nrow=2,heights=c(2,1))))
print(ggplot(star.logs.unmapped,
             aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
      + geom_boxplot()
      + facet_grid(field~.,scales="free")
      + ylab("Percent of Reads")
      + xlab(NULL)
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,0,0,1.1),"strwidth",data=list("","","","e8")),
              axis.title.x=element_blank(),
              axis.text.x = element_blank()),#element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=1)
      )
pushViewport(viewport(layout.pos.col=1,layout.pos.row=1))
grid.text("A",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport()          
print(ggplot(star.logs[grepl("input reads$",field),],
             aes(x=capfirst(species),y=as.numeric(value)))
      + geom_boxplot()
      + scale_y_log10()
      + ylab("Reads")
      + xlab("Species")
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,1.6,0,0),"strheight",data=list("","TO","","")),
              axis.text.x = element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=2))
pushViewport(viewport(layout.pos.col=1,layout.pos.row=2))
grid.text("B",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport(2)
@ 
\caption{RNAseq read and alignment statistics for all species. A)
  Boxplot of percentages of unmapped reads in each species; 0\% of
  reads in all species were unmapped because of mismatches. B) Boxplot
  of number of RNAseq reads in each species.}
\label{fig:transcriptome_statistics}
\end{figure}

>>>>

% \begin{figure}
% <<transcriptome.mapping.figure,fig.width=8,fig.height=8,echo=FALSE>>=
% star.logs.unmapped <- 
%     star.logs[grepl("%",field) & 
%                   grepl("unmapped",field) & 
%                       !grepl("too many mismatches",field),]
% star.logs.unmapped <- 
%     star.logs.unmapped[,field:=capfirst(gsub("\\% of reads unmapped: ","",field))]
% pushViewport(viewport(layout=grid.layout(ncol=1,nrow=2,heights=c(2,1))))
% print(ggplot(star.logs.unmapped,
%              aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
%       + geom_boxplot()
%       + facet_grid(field~.,scales="free")
%       + ylab("Percent of Reads")
%       + xlab(NULL)
%       + theme_bw()
%       + theme(legend.position="top",
%               plot.margin=unit(c(0,0,0,1.1),"strwidth",data=list("","","","e8")),
%               axis.title.x=element_blank(),
%               axis.text.x = element_blank()),#element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
%       vp=viewport(layout.pos.col=1,layout.pos.row=1)
%       )
% pushViewport(viewport(layout.pos.col=1,layout.pos.row=1))
% grid.text("A",
%           y=unit(1,"npc")-unit(0.1,"cm"),
%           x=unit(0,"npc")+unit(0.1,"cm"),
%           gp=gpar(fontsize=24),
%           just=c("left","top"))
% popViewport()          
% print(ggplot(star.logs[grepl("input reads$",field),],
%              aes(x=capfirst(species),y=as.numeric(value)))
%       + geom_boxplot()
%       + scale_y_log10()
%       + ylab("Reads")
%       + xlab("Species")
%       + theme_bw()
%       + theme(legend.position="top",
%               plot.margin=unit(c(0,1.6,0,0),"strheight",data=list("","TO","","")),
%               axis.text.x = element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
%       vp=viewport(layout.pos.col=1,layout.pos.row=2))
% pushViewport(viewport(layout.pos.col=1,layout.pos.row=2))
% grid.text("B",
%           y=unit(1,"npc")-unit(0.1,"cm"),
%           x=unit(0,"npc")+unit(0.1,"cm"),
%           gp=gpar(fontsize=24),
%           just=c("left","top"))
% popViewport(2)
% @ 
% \caption{RNAseq read and alignment statistics for all species. A)
%   Boxplot of percentages of unmapped reads in each species; 0\% of
%   reads in all species were unmapped because of mismatches. B) Boxplot
%   of number of RNAseq reads in each species.}
% \label{fig:transcriptome_statistics}
% \end{figure}
